Inferring Invariants of Distributed Programs

### 2015-03-03 Doc/paper.tex
v1 approach

The ultimate goal of this project is to infer invariants in a distributed system. For that we need to identify likely distributed state variables. We define distributed state variables,  as variables that are stored in one node whose values are affected/determined by another remote node in the distributed system. It should be noted that these variables are only a part of the state in a distributed system at a given time. For our case we assume that these capture a significant portion of the state. Consider the code samples Listing~\ref{lst:node0} and Listing~\ref{lst:node1} showing the communication between two nodes in a distributed system. The communication between the nodes can be depicted as shown in Figure~\ref{fig:sample_code_diag}. We need to infer the equality between elements in each pair \texttt{(a,first), (b,second),(sum,result)} and also the properites: \texttt{(result = a + b)} and \texttt{(sum = first + second)}.

@@

@@

To detect these variables, some form of dataflow analysis is required. This includes the dataflow of the distributed system as a whole and also in a single program. But currently there are no data flow analysis frameworks available for Go programs.

@@

>>>>

The ultimate goal of this project is to infer invariants in a
distributed system. For the scope of this project we will consider a system with 2 nodes. Before inferring invariants we need to identify likely distributed
state variables. We define distributed state variables, as variables
that are stored in one node whose values are affected or determined by
the other remote node in the distributed system. It should be noted that
these variables are only a part of the state in a distributed system
at a given time. For our case we assume that these capture a
significant portion of the state. Consider the code samples
Listing~\ref{lst:node0} and Listing~\ref{lst:node1} showing the
communication between two nodes in a distributed system. The
communication between the nodes can be depicted as shown in
Figure~\ref{fig:sample_code_diag}. We need to infer the equality
between elements in each pair \texttt{(a,first),
(b,second),(sum,result)} and also the properites: \texttt{(result = a
+ b)} and \texttt{(sum = first + second)}.

@@

The naive approach for inferring these invariants will be to dump all
state varaible values at all program points and feed them to an
invariant detector like daikon\cite{ernst2007daikon}. But given the
number of program points and huge number of variables in a relatively
large program this approach is not scalable. So we propose 2 main
optimizations to reduce the number of program point, variable value
combinations.

\subsection{Detecting interesting program points}

Rather than dumping state at all program points we expect the
developer to mark interesting program points using annotations. The
program state will be dumped at only these annotated points. This will
also help to narrow down the focus to points that are identified by
the developer as interesting points without wasting resources
analyzing useless program points. The annotations will be identified
by the parser at the instrumentation phase and re-written to include
statements which will write the values of variable to a file when the
program reaches that point in the runtime.

@@

Even at interesting program points, variable space that need to be
captured is very large. So only the variables that were affected by
the communication with other nodes need to be identified. To detect
these variables, some form of dataflow analysis is required. This
includes the dataflow of the distributed system as a whole and also in
a single program. But currently there are no data flow analysis
frameworks available for Go programs.

@@

\subsection{Timeline}
